Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-08-18 docs/00-manuscripts/ieee/reviews/review2/reviewer2-reply.md

Thanks for suggesting possible improvements to Figure 3.
We omitted the unit for RMSE in all other tables/figures.
Adding it only here would make things inconsistent.
We believe that it should be clear to readers of the study that the unit is percentage points as it is mentioned in various places.

Lasso and Ridge were appended with a "MBO" suffix to highlight the use of MBO for internal optimization in contrast to using their respective integrated tuning algorithms.
The added value might not be fully clear, hence we removed the suffix.

We have changed the color palette to "Viridis", a palette with support for colorblind people.

> P9, Figure 4: The filters improved the results mainly for the task HR. For all others, the no Filter results are within the best results. Please explain how can a filter worsen the performance?

Thanks for the detailed look on the results.
There is no guarantee that the use of filters always improves the result, even though the selection of features is optimized via tuning.
As mentioned and discussed in the study, the outcome is a combination of learner+dataset+filter and using a subset of features might not always result in the best performance.
Also the ranking of certain filters might simply not have a positive effect and result in features being removed even though they would have been helpful to the model in the end.

> P9, Figure 5: Why did you highlight Borda Filter?

 We highlighted the Borda filter because the use of ensemble filters (i.e. the Borda filter) is a central evaluation point of this work.

> P10, Figure 6: As I mentioned in the general comments you have to apply smoothing before analyzing the spectral signatures. The peak around 950nm is also very strange.

Please see our previous comment on this topic.

> What does scaled Reflectance or in the caption normalized reflectance mean?

Normalized reflectance between [0, 1] as shown on the axis title.

> P11, C1, L47: not instead of no

Thanks.

> P11, C1, L56-58: PCA obtained the worst results!

Thanks for double-checking the results.
Indeed PCA scored the worst results and this is what we wrote in l.52 - 56.
It also reduced model fitting times, which is fair to mention.

> P11, C2, L10-11: Instead of “not surprisingly” I would prefer citing other studies which obtained similar results.

Using references to support statements is usually a good idea.
In this case however, we believe that this statement does not need to backed by additional references.

> P11, C2, L36-37: Sentence is not necessary.

Thanks, we removed it.

> P11, C2, L48: Why only in almost all cases. I don’t see an option to get less or more pixels. Anyway, this approach is not a solution for your mentioned problem of pixels outside the tree. On the contrary, the method leads to the fact that neighboring pixels are included.

We agree that there are no possibilities to get a different number of pixels than exactly four and removed "almost" from the sentence.

As mentioned in previous comments, we still believe that this approach is a good compromise for the issue at hand.

> P13, C1, 56: Please avoid citations in the conclusion.

We tried to avoid or at least minimize the number of citations in the Conclusion, but we find this one reference particularly pertinent.

> The appendix is often not mentioned in the manuscript except Table VIII.

That's why the resources are listed in the appendix.

> Why do some of the Figures and Tables have regular numbering and some not?

As mentioned we are using the IEEE Tran Latex class and numbering is determined by such.
